### 2014-12-01 text/Chapter06.tex
Proofreading chapters 1 and 2, reorder chapter 6

Although the results presented in this thesis are mainly of a theoretical nature, we indeed 
believe that coeffects should be integrated in main-stream programming languages. In the second
part of this chapter, we outline one possible approach for practical implementations of coeffects 
(Section~\ref{sec:unified-impl}). Finally, we discuss an alternative approach to defining coeffect 
systems which highlights the relationship between our work and related work arising from modal logics 
(Section~\ref{sec:unified-meta}).

>>>>

Although the results presented in this thesis are mainly of a theoretical nature, we indeed 
believe that coeffects should be integrated in main-stream programming languages. In the second
part of this chapter, we discuss an alternative approach to defining coeffect 
systems which highlights the relationship between our work and related work arising from modal logics 
(Section~\ref{sec:unified-meta}). Finally, we outline one possible approach for practical
implementations of coeffects (Section~\ref{sec:unified-impl}).
